
\chapter*{Abstract}

The thesis was born trying to combine two of the most promising developing areas in the today technology industry: blockchain and 
process mining. The first one is a revolutionary technology that has the potential to fundamentally change many industries, 
which include banking, music, publishing industry, job trading and many others. Even big companies like Amazon and Microsoft 
are investing in this technology. On the other side process mining and more in detail process mining discovery 
techniques allow to infer information starting from the analysis of a log file to understand how running systems work.

The main goal of the thesis is to apply process mining discovery algorithms to blockchain transaction in order to infer the 
logic behind a smart contract.

The first step addressed was the creation of a solid background, deepening the literature about process mining, the general 
priciples at the base of the blockchain and official documentation of Ethereum. Ethereum was chosen 
because of its flexibility and its capability to be general purpose, in fact it can be used in a lot of different application 
domains.

Then we select a set of algorithms such as Split Miner, Inductive Miner and Heuristic Miner to apply to some logs created from 
Ethereum transactions. With these we found and studied in detail three case studies. Two of these case study are games while the 
third is a cryptocurrency Exchange. 

Finally, we have implemented a system that has two main components: it allows users to query ethereum in order to get aggregated 
data stored in the blockchain and to extract a process model from a log with a specific format. The query section has value in 
itself but can also be seen as preparatory for the mining part.