\chapter{Conclusions and future works}

In general the importance of process mining for industries is known because  it allow to reduce costs, optimize resource 
handling and how the work is done. Over that it also allows to assist the live execution of the process with predictions 
(as for example completation time or the next choice).

Blockchain has a huge potential and it can change a lot of business areas despite it is still a quite immature technology. 
In last times great investments has been made on this technology even from huge companies  and this means that its 
development will be really fast in next years.

The work done in this thesis shows that is possible, combining the processing power of process mining and the execution power 
of the blockchain, to infer the logic behind systems that uses Ethereum as decentralized server. This consideration can have a 
lot of future developments: for example companies can provide a validity check service for applications resident on the 
blockchain. The blockchain transparency itself can be enhanced by the combination of these two technologies because people or 
organizations external to the application domain can check the correctness of the behaviour of the system. Also the same 
developers can use these techniques to test their applications. Another interesting use case could be the extraction of the 
system structure in order to express it in a format understandable from company managers even if they have not technical 
competence. Obviously all this transparency can also be seen from a negative point of view: if a company has built its 
competitive advantage towards competitors thanks to advanced business logic the possibility that someone else can deduce this 
logic and reduce the market gap is certainly a negative aspect that can lead companies to be wary of this type of technologies.

With the design and implementation part, a prototype of a tool was created that allows the user in a few steps to perform 
analysis on the blockchain. There are many possible future developments such as the addition of new algorithms, the export 
from the server of an already rendered image of the petri net, the export from Querying Ethereum directly to XES, etc.